% !TEX encoding = UTF-8 Unicode
\documentclass[a4paper,12pt]{article}
\usepackage[T1, OT1]{fontenc}
\usepackage{hyperref}
\DeclareTextSymbolDefault{\dh}{T1}
\include{cv-commands}


\begin{document}

\centerline{\Huge Curriculum Vitae \vspace*{5mm}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\header
{Jóannes í Sandagerði}
{}
{Skodsborgvej 190, st, vær 2902
2850 Nærum, Denmark
Email: joannesis@gmail.com
\href{http://linkedin.com/in/joannesisandagerdi}{linkedin.com/joannesisandagerdi}
Tel: \smcp{(+45) 52 71 70 10}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \begin{objective}{Profile}
% {
% contains a sentence or two about the type of work you are aiming for.
% a few lines about the attributes which make you suitable for the role.
% You can even call it nothing at all. If it's in the usual place at the start of the CV you can just have an un-named paragraph.
% I am a confident, hands-on software engineer that is not afraid to
% I have
% Skilled tester,
% Detail-oriented, able to discover issues
% Video validation
% Confident with Linux systems and script programming. Have create
% }
% \largeskip
% \end{objective}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{resumeblock}{Education}

\resumeitem{2013--2015}{\textbf{MSc in Computer Science and Engineering} at Technical University of Denmark.\newline
Specializing in Software Engineering.\newline
Additionally, taken courses in Data Security, Network Security and special course Practical Network Security.}
\largeskip

\resumeitem{2010--2012}{\textbf{Bachelor of Information Technology} at Queensland University of Technology in Brisbane, Australia.\newline
Specialized in Software Engineering and Networks.\newline
Course GPA 6.0 on a 7-point scale, graduated with Distinction \href{http://www.mopp.qut.edu.au/C/C_05_02.jsp}{(Scale)}}

\largeskip

\end{resumeblock}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Professional experience}

\resumeitem{Dec 2014 - Present}{\textbf{Software Developer} at Cimco Integration in Copenhagen, Denmark.\newline
Software Developer where majority of the work is in C++.\newline
- Tasks include maintaining existing codebase, and implementing new features.}
\largeskip

\resumeitem{May 2013--Aug 2013}{\textbf{Localisation and Quality Assurance Engineer – Danish speaking} at Apple, Inc. in Cork, Ireland.\newline
Summer position as a QA Tester for Danish language.\newline
- QA testing of Apple's software in Mac OS X, iOS and Windows environments.\newline
- Developing scripts and utilities for automating the test environment.\newline
- Issue discovery, reporting, and regression testing.}
\largeskip

\resumeitem{Mar 2012--May 2012}{\textbf{Java Developer Intern} at Red Hat, Inc. in Brisbane, Australia.\newline
Developed a tool for the Documentation team in the Brisbane Office.\newline
- Java, EJB, HTLM, JavaScript tool used for comparing versions of Red Hat XML based Documentation.\newline
- The tool could generate management reports on differences measured between documents.}
\largeskip

\resumeitem{Jul 2010--Nov 2010}{\textbf{Peer Assisted Study Session Leader} at Queensland University of Technology.\newline
Study Session leader for an Introduction to Programming unit, where programming language was Python.\newline
- Developed study material, and assisted students with assignments.
}
\largeskip

\resumeitem{Nov 2008--Dec 2009}{\textbf{Localisation and Quality Assurance Engineer – Danish speaking} at Apple, Inc.
Responsible of QA testing Apple software products for Danish language issues.
- See above.
- Wrote test case guides for testers.
- Wrote scripts for automatic detection of common internationalization mistakes across Apple software.}
\largeskip
\end{resumeblock}

% \newpage

\begin{resumeblock}{Technical skills}

\resumeitem{Programming}{Java, C++, C\#, Python, Design Patterns, UML design, Git}
\largeskip

\resumeitem{Web technologies}{HTML, PHP, JavaScript, SQL, CSS}
\largeskip

\resumeitem{Operating Systems}{Mac OS X, various Linux distributions, Windows, iOS, Android}
\largeskip

\resumeitem{Recent interests}{Linux Systems, Amazon EC2, VPS}

\end{resumeblock}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Projects}

\resumeitem{2014 - Present}{Java Application. Developed a project management tool, to be used by translators. Features include creating and tracking clients/jobs, generating reports, viewing earnings.}
\largeskip

\resumeitem{2014}{Android Application. Developed an application, that enabled the phone to be remote controlled by a web service (WS), for a home security system. The phone could act as either a sensor or actor, depending on configuration received from the WS, and would transmit video/sensor readings to the WS.}
\largeskip

\resumeitem{2013}{Wrote an application for a Linux server that allowed me to remote control it by sending email messages to a specific address.
}
\largeskip

\resumeitem{2013}{Developed a Facebook chat bot that could analyse incoming messages and appropriately reply with a predefined answer: e.g. Q: ``What's your phone number'' A: ``PHONENUMBER'', Q: ``Translate: How are you?'' A: ``¿Cómo estás?''}
\largeskip
\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Languages}
\resumeitem{Fluent}{English, Danish, and Faroese}
\shortskip
\resumeitem{Can converse}{Swedish and Norwegian}
\largeskip
\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{References}
\resumeitem{Apple, Inc.}{\textbf{Dave Wiley}
European Localization  Quality Manager\newline
wiley.coyote@apple.com\newline
+353 21 4284370 or +353 87 9370436
}
\largeskip

\resumeitem{Red Hat, Inc.}{\textbf{Michael Doyle}
Supervisor at Red Hat\newline
mdoyle@redhat.com\newline
+61 7 3514 8216}
\end{resumeblock}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}



% \begin{interestsblock}{Interests \& activities}
% 	\interest{idea}{Political philosophy and Foreign Affairs} &
% 	\interest{gnu}{Free Software Movement}\\
% 	&\\
% 	\interest{hack}{Solving problems} &
% 	\interest{bike}{Cycling!}
% \end{interestsblock}
